---
title: "Untitled"
author: "sadie"
date: "9/20/2019"
output: html_document
---
Here we're trying to compare branch length estimates across the three models, MG94, MG94x2, and MG94x3. This involves large datasets and just a lot of data clean up and formatting

```{r, message=FALSE, warning=FALSE,}
library(readr)
library(dplyr)
library(ggplot2)
library(stringr)
library(plotly)
```

```{r load libraries and data, message=FALSE, warning=FALSE, cache=TRUE}




selectome.dat <- read_csv("~/Downloads/SELECTOME_TREELENGTHS_BRANCHLENGTHS.csv")

sites.dat <- read_tsv("~/Downloads/SELECTOME_MUTATIONS_BRANCH_SITE.tsv")


```
## make file names matchable
```{r, cache=TRUE}
sites.dat$`File name` <- sites.dat$Filename %>% str_remove(., ".FITTER.json")
```

## create entry for individual branches
```{r, cache=TRUE}
library(tidyr)

temp.1 <- sites.dat %>% separate_rows(.,Branch,sep =",")

"{'0': 'PHLDB1_CAVPO'}" -> x

temp.1$Branch <- temp.1$Branch %>% str_remove(., "\\{") %>% str_remove(., "\\}") %>% str_remove_all(., "'") %>% 
  str_remove('[0-9]: ') %>% str_trim()
```


## put branch length estimates for each model in own column for each branch 
## Lengthx1 - the branch length according to Standard MG94
## Lengthx2 - the branch length according to the double hit MG94
## Lengthx3 - the branch length according to the triple hit MG94
```{r, cache=TRUE}
attach(selectome.dat)
temp.2 <- selectome.dat %>% separate_rows(., `Branch Attributes - MG94 with double and triple instantaneous substitutions`,`Branch Attributes - MG94 with double instantaneous substitutions`, `Branch Attributes - Standard MG94`, sep = ",")

temp.2 <- temp.2 %>% separate(`Branch Attributes - MG94 with double and triple instantaneous substitutions`, c("Branchx3", "Lengthx3"), sep = ":", convert = TRUE)

temp.2 <- temp.2 %>% separate(`Branch Attributes - MG94 with double instantaneous substitutions`, c("Branchx2", "Lengthx2"), sep = ":", convert = TRUE)

temp.2 <- temp.2 %>% separate(`Branch Attributes - Standard MG94`, c("Branchx1", "Lengthx1"), sep = ":", convert = TRUE)


temp.2$Branch <- temp.2$Branchx3 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim()


temp.2$Lengthx1 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim() -> temp.2$Lengthx1

temp.2$Lengthx2 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim() -> temp.2$Lengthx2

temp.2$Lengthx3 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim() -> temp.2$Lengthx3
```



## combine data.frame with mutation type information with p value and other stats and parameter info data.frame
## this is huge ~3GB (could remove some columns I don't immeadiately use)
```{r}
temp.3 <- right_join( temp.2, temp.1, by = c("File name","Branch"))


#as.numeric(temp.3$Lengthx3) %>% is.na() %>% which()
#temp.2$Lengthx3[14302]

#temp.3 %>% select(`File name`, Branch, Lengthx1,Lengthx2, Lengthx3, `Mutation Type`, `Double-hit vs single-hit - p-value`,`Triple-hit vs single-hit - p-value`,`Triple-hit vs double-hit - p-value`) %>% write_csv(., "Branch_lengths_small.csv")
#write_csv(temp.3, "Branch_lengths.csv")
```



```{r, eval=FALSE}
temp.3 %>% ggplot(aes(x = as.numeric(Lengthx3), y = as.numeric(Lengthx1)))+geom_point(aes(color = `Mutation Type`))+coord_cartesian(xlim = c(0,1), ylim = c(0,1))
```

## create a data.frame with all the length estimates in one column for easier graph amking
```{r, cache=TRUE}
library(reshape2)
 #temp.3 %>% select(`File name`, Branch, Lengthx1,Lengthx2, Lengthx3, `Mutation Type`)%>% head()
temp.4 <- temp.3 %>% select(`File name`, Branch, Lengthx1,Lengthx2, Lengthx3, `Mutation Type`, `Double-hit vs single-hit - p-value`,`Triple-hit vs single-hit - p-value`,`Triple-hit vs double-hit - p-value`)  %>%  melt(id.vars = c("File name","Branch", "Mutation Type", "Double-hit vs single-hit - p-value","Triple-hit vs single-hit - p-value", "Triple-hit vs double-hit - p-value"), variable.name = "Length_by_Model", value.name = "Length_Est") 
#write_csv(temp.4, "Branch_lengths_melted.csv")
```

## Boxplots of estimates branch length grouped by Model and colored by mutation type
## Mutation type:
## SH - a single hit mutation occur on the branch
## DH - a double hit mutation occurred on the branch
## TH - a triple hit mutation occured on the branch
```{r}
temp.4 %>% ggplot() + geom_boxplot(aes(x=Length_by_Model, y = as.numeric(Length_Est), color = `Mutation Type`))+ ylim(0,1)
```
## Boxplots of estimates branch length grouped by mutation type and colored by Model
```{r}
temp.4 %>% ggplot() + geom_boxplot(aes(x=`Mutation Type`, y = as.numeric(Length_Est), color = Length_by_Model))+ ylim(0,1)
```

## histograms with bin size 0.01 for DH and TH branch length distribution. SH not included because there are soooo many more of them. 
```{r}
temp.4 %>% filter(`Mutation Type` != "SH") %>%  ggplot() + geom_histogram(aes(x = as.numeric(Length_Est), y = (..count..)/sum(..count..), fill =Length_by_Model), position = "dodge", binwidth = 0.01)+ facet_grid(~`Mutation Type`, scales = "free_y")+ xlim(0,0.5)
```


## Frequency plots can see how many SH there are. I feel like these both show that all 3 models estimate length very closely and that all 3 substitution types have a similar distribution of branch lengths
```{r}
temp.4 %>% ggplot() + geom_freqpoly(aes(x =as.numeric(Length_Est), y = (..count..)/sum(..count..), color =Length_by_Model), position = "dodge", binwidth = 0.01)+ facet_grid(~`Mutation Type`)+ xlim(0,0.5)
```


## scatter plot for MG94x3 vs MG94x2 with p <= 0.05.  Line is x = y 
```{r}
temp.3 %>% filter(`Triple-hit vs double-hit - p-value` <= 0.05) %>% ggplot()+geom_point(aes(x = as.numeric(Lengthx3), y= as.numeric(Lengthx2), color = `Mutation Type`)) + coord_cartesian(xlim = c(0,5), ylim = c(0,5))+geom_abline(slope = 1, intercept = 0)
```

## scatter plot for MG94x3 vs MG94x1 with p <= 0.05.  Line is x = y 
```{r}
temp.3 %>% filter(`Triple-hit vs single-hit - p-value` <= 0.05) %>% ggplot()+geom_point(aes(x = as.numeric(Lengthx3), y= as.numeric(Lengthx1), color = `Mutation Type`)) + coord_cartesian(xlim = c(0,5), ylim = c(0,5)) + geom_abline(slope = 1, intercept = 0)+facet_grid(.~`Mutation Type`)

```

```{r}

sh.branches <- temp.1 %>% filter(`Mutation Type` == "SH") 
dh.branches <- temp.1 %>%  filter(`Mutation Type` == "DH")
th.branches <- temp.1 %>% filter(`Mutation Type` == "TH")

```

which files have branches with single and double hits for the same file?
```{r}
sh.dh.files <- dh.branches$`File name`[which(paste(dh.branches$Branch, dh.branches$`File name`) %in% paste(sh.branches$Branch, sh.branches$`File name`))]

sh.dh.files <- dh.branches$`File name`[which(paste(dh.branches$Branch, dh.branches$`File name`, dh.branches$`Site Position`) %in% paste(sh.branches$Branch, sh.branches$`File name`, sh.branches$`Site Position`))]
```

which files have branches with single and triple hits for the same file?

```{r}
sh.th.files <- th.branches$`File name`[which(paste(th.branches$Branch, th.branches$`File name`) %in% paste(sh.branches$Branch, sh.branches$`File name`))]

sh.th.branches <- th.branches$Branch[which(paste(th.branches$Branch, th.branches$`File name`) %in% paste(sh.branches$Branch, sh.branches$`File name`))]
```


which files have branches with double and triple hits for the same file?

```{r}
dh.th.files <- th.branches$`File name`[which(paste(th.branches$Branch, th.branches$`File name`) %in% paste(dh.branches$Branch, dh.branches$`File name`))]

dh.th.sites<- th.branches$`File name`[which(paste( th.branches$`File name`, th.branches$`Site Position`) %in% paste( dh.branches$`File name`, dh.branches$`Site Position`))]
```

want to compare sh value for branch to double hit value for the same branch

```{r}
u <- temp.3 %>% select(`File name`,`Triple-hit vs single-hit - p-value`, Lengthx1, Lengthx3,Branch) %>% filter(`File name` %in% sh.th.files, Branch %in% sh.th.branches) %>% mutate(diff.sh.th = as.numeric(Lengthx1) - as.numeric(Lengthx3), per.diff.sh.th = abs(as.numeric(Lengthx1) - as.numeric(Lengthx3))/as.numeric(Lengthx1)) 

u %>% ggplot() + geom_histogram(aes(x= diff.sh.th)) + xlim(-0.005,0.05)

u %>% ggplot() + geom_freqpoly(aes(x= per.diff.sh.th)) +xlim(0,0.2) 

write_csv(u, "th_v_sh_branch_difs.csv")
```

#previous code
```{r, eval=FALSE}

output_withcol %>% filter(`Triple-hit vs double-hit - p-value`<=0.05) %>% ggplot(aes(x = `Tree Length - MG94 with double and triple instantaneous substitutions`, y = `rate at which 3 nucleotides are changed instantly within a single codon`))+geom_point()+coord_cartesian(xlim = c(0,10), ylim = c(0,10))


output_withcol %>% filter(`Triple-hit vs double-hit - p-value`>0.05) %>% ggplot(aes(x = `Tree Length - MG94 with double and triple instantaneous substitutions`, y = `rate at which 3 nucleotides are changed instantly within a single codon`))+geom_point()+coord_cartesian(xlim = c(0,10), ylim = c(0,10))
```

```{r, eval=FALSE}
output_withcol %>% filter(`Triple-hit vs double-hit - p-value`<=0.05) %>% select(`File name`)

 temp <- output_withcol %>% filter(`Triple-hit vs double-hit - p-value`<=0.05, `File name` == "ENSGT00680000099768.Euteleostomi.004.nex") %>% select(`Branch Attributes - MG94 with double and triple instantaneous substitutions`, `Branch Attributes - MG94 with double instantaneous substitutions`) 

temp$`Branch Attributes - MG94 with double and triple instantaneous substitutions`  %>% str_remove_all(.,"\\{") %>% str_remove_all(.,"\\}")%>% str_split(., ",") -> x

x %>% lapply(., function(x) str_split(x, ":") ) %>% unlist -> x

cols <-c("branch", "length.triple")

matrix(unlist(x),ncol=2,byrow=TRUE, dimnames = list(NULL, cols)) -> temp.triple

temp$`Branch Attributes - MG94 with double instantaneous substitutions`  %>% str_remove_all(.,"\\{") %>% str_remove_all(.,"\\}")%>% str_split(., ",") -> x

x %>% lapply(., function(x) str_split(x, ":") ) %>% unlist -> x

cols <-c("branch", "length.double")
matrix(unlist(x),ncol=2,byrow=TRUE, dimnames = list(NULL, cols)) -> temp.double


x <- full_join(as.data.frame(temp.double, stringsAsFactors = F), as.data.frame(temp.triple, stringsAsFactors = F), by = "branch")

x[, 2:3] <- as.numeric(unlist(x[,2:3]))
```



