---
title: "BUSTED_MH"
author: "sadie"
date: "1/10/2020"
output:
  pdf_document: default
  html_document: default
---
```{r, message=FALSE, warning=FALSE,}
library(readr)
library(dplyr)
library(ggplot2)
library(stringr)
library(plotly)
library(tidyr)

```

load data
```{r load libraries and data, message=FALSE, warning=FALSE, cache=TRUE}

BUSTED_MH <- read_csv("~/Downloads/selectome_subset_THvDH_1_10_2020")

BUSTED.SRV.dat.selectome <- read_csv("~/Downloads/BUSTED-SRV_selectome_5_20_19")

BUSTED.dat.selectome <- read_csv("~/Downloads/BUSTED_selectome_5_20_19")
```

get basenames for files since full paths aren't going to match
```{r}
BUSTED_MH$basename <- BUSTED_MH$FILE %>% basename()

BUSTED.SRV.dat.selectome$basename <-BUSTED.SRV.dat.selectome$FILE %>% basename()

BUSTED.dat.selectome$basename <-BUSTED.dat.selectome$FILE %>% basename()
```

create one df with both BUSTED[SMH] and BUSTED[S] results matching the results by basename, number of sites and number of sequences. 
```{r}
dat <- inner_join(BUSTED_MH,BUSTED.SRV.dat.selectome,  by = c("basename", "Sites", "Sequences"), suffix = c(".MH",".SYN"))

dat.sel <- inner_join(BUSTED.dat.selectome,BUSTED.SRV.dat.selectome, by = c("basename", "Sites", "Sequences") )%>% filter(basename %in% BUSTED_MH$basename)

dat_3 <- inner_join(dat, BUSTED.dat.selectome, by = c("basename", "Sites", "Sequences"))

attach(dat)
```

line is x = y 
```{r}
dat %>% ggplot() + geom_point(aes(x=BUSTED.SRV.P.MH, y = BUSTED.SRV.P.SYN)) + geom_abline(slope = 1, intercept = 0)
```
BUSTED[S] p values are typically lower than BUSTED[SMH] p values

```{r}
dat %>% ggplot() + geom_histogram(aes(x = BUSTED.SRV.P.MH), fill = "red", alpha = 0.5, binwidth = 0.01) + 
  geom_histogram(aes(x = BUSTED.SRV.P.SYN), fill = 'blue' , alpha = 0.5, binwidth = 0.01)
```

```{r}
pairs(data = dat, ~ CV.SRV.MH + CV.SRV.SYN + srv.omega.3.rate.MH + srv.omega.3.rate.SYN)
```


oh how do the two way tables compare???

```{r}
source("/Volumes/GoogleDrive/My Drive/BUSTED-SRV/R/useful_functions.R")

gen.sig.table.mh <- function(dat = x, p = 0.05, Bon = FALSE){
  #prints out a table that tells what proportion of data files
  #are under selection/not under selection according to BUSTED
  #and BUSTED+SRV
  require("xtable")
  library("xtable")
  
  #bonferroni correction
  if(Bon ==TRUE){
  alpha <- p/nrow(dat)
  }
  if(Bon == FALSE){
    alpha <- p
  }
  
  under.sel.busted = which(dat$BUSTED.SRV.P.MH<=alpha)
  under.sel.srv = which(dat$BUSTED.SRV.P.SYN<=alpha)
  
  
  mat = matrix( rep(0),nrow=length(dat$BUSTED.SRV.P.MH),ncol = 2,
                dimnames= list(1:length(dat$BUSTED.SRV.P.MH),
                               c("BUSTED[MH]", "BUSTED[S]")))
  mat[under.sel.busted,1] = 1
  mat[under.sel.srv,2] = 1 
  sel.tab = table(mat[,1],mat[,2], dnn = colnames(mat))
  t.names <- c("No Selection", "Selection")
  row.names(sel.tab) <- t.names[rownames(sel.tab) %>% as.numeric()+1]
  colnames(sel.tab) <- t.names[colnames(sel.tab) %>% as.numeric()+1]
  Sel.Prop =prop.table(sel.tab)
  test.table = xtable(Sel.Prop)
 
 
  print.xtable(test.table, type = "latex", file = "sel_table.txt")
  return(Sel.Prop)
}

dat %>% gen.sig.table.mh()
```

so about 19% of the data sets are under selection according to BUSTED[S] but not BUSTED[SMH].

```{r}
dat.sel %>% gen.sig.table()
```

about 15% of the data sets are under selection according to BUSTED but not BUSTED[S]. Overall, more data sets have no evidence of positive selection according to both tests for BUSTED[S] and BUSTED[SMH] verse BUSTED and BUSTED[S]


three-way comparison of p values
```{r}
library(reshape2)

dat_3 %>% melt(measure.vars = c("BUSTED.P", "BUSTED.SRV.P.MH", "BUSTED.SRV.P.SYN"), id.vars = c("basename", "Sites", "Sequences")) -> temp

temp %>% ggplot()+ geom_boxplot( aes(y = value, x = variable))
```


or violin plot
```{r}
temp %>% ggplot()+ geom_violin( aes(y = value, x = variable))
```

basically shows that for BUSTED[SMH] p values are skewed much higher in comparison to both BUSTED and BUSTED[S]