---
title: "Example alignments"
author: "sadie"
date: "2/5/2020"
output:
  pdf_document: default
  html_document: default
---

```{r, message=FALSE, warning=FALSE,}
library(readr)
library(dplyr)
library(ggplot2)
library(stringr)
library(plotly)
library(tidyr)
```


```{r}
ex <- read_csv("~/Downloads/example_alignments_2_5_2020.csv")
```
```{r}
dh <- which(ex$`Double-hit vs single-hit - p-value`<=0.05) %>% ex$`File name`[.]
dh
```

```{r}
th <- which(ex$`Triple-hit vs double-hit - p-value`<=0.05) %>% ex$`File name`[.]
th
```

```{r}
thi <- which(ex$`Triple-hit vs Triple-hit-island - p-value`<=0.05) %>% ex$`File name`[.]
thi
```
```{r}
th.dh <- intersect(th,dh)
```
these files `r th.dh` are 

```{r}
only.dh <- setdiff(dh,th)
only.dh
```

```{r}
temp <- ex %>% filter(`File name` %in% only.dh) %>% select(`File name`,starts_with("rate at which"))
```


read in json for Influenza A
```{r}
library(jsonlite)
InfA <- fromJSON("~/Downloads/example_alignments/data/InfluenzaA.nex.FITTER.json")
HIV_RT <- fromJSON("~/Downloads/example_alignments/data/HIV_RT.nex.FITTER.json")
```

```{r}
InfA$`Site Log Likelihood`$`MG94 with double instantaneous substitutions` %>% which.min() 

HIV_RT$`Site Log Likelihood`$`MG94 with double instantaneous substitutions` %>% which.min() 

InfA$`Evidence Ratios`$`Two-hit` %>% max()
InfA$`Evidence Ratios`$`Two-hit` %>% min()
InfA$`Evidence Ratios`$`Two-hit` %>% mean()


InfA$`Evidence Ratios`$`Three-hit` %>% max()
InfA$`Evidence Ratios`$`Three-hit` %>% min()
InfA$`Evidence Ratios`$`Three-hit` %>% mean()

InfA$`Evidence Ratios`$`Three-hit islands vs 2-hit` %>% max()
InfA$`Evidence Ratios`$`Three-hit` %>% min()
InfA$`Evidence Ratios`$`Three-hit` %>% mean()
```
```{r}
HIV_RT$`Evidence Ratios`$`Two-hit` %>% max()
HIV_RT$`Evidence Ratios`$`Two-hit` %>% which.max()
HIV_RT$`Evidence Ratios`$`Two-hit` %>% min()
HIV_RT$`Evidence Ratios`$`Two-hit` %>% mean()
HIV_RT$`Evidence Ratios`$`Two-hit` %>% median()


HIV_RT$`Evidence Ratios`$`Three-hit` %>% max()
HIV_RT$`Evidence Ratios`$`Three-hit` %>% min()
HIV_RT$`Evidence Ratios`$`Three-hit` %>% mean()
HIV_RT$`Evidence Ratios`$`Three-hit`[163]

HIV_RT$`Evidence Ratios`$`Three-hit vs three-hit islands`[163]

HIV_RT$`Evidence Ratios`$`Three-hit islands vs 2-hit` %>% max()
HIV_RT$`Evidence Ratios`$`Three-hit` %>% min()
HIV_RT$`Evidence Ratios`$`Three-hit` %>% mean()
```
|   Site   |       ER (2 vs 1)       |       ER (3 vs 2)       |   ER (3-island vs 2)    |   ER (3-island vs 3)    |                       Substitutions                        |
|:--------:|:-----------------------:|:-----------------------:|:-----------------------:|:-----------------------:|:----------------------------------------------------------:|
|    48    |         106.3661        |           0.7761        |           0.9988        |           0.7770        |ACA->AAA(1), TCA->AAA(4)ACA(8)CAA(1)GAA(2)TCC(1)TCG(2), T...|
|    64    |          13.1124        |           0.9154        |           0.9885        |           0.9261        |  AAA->AAA(2), AAG->AAA(8)AGG(5)CAC(1)TCG(1), AGG->AAA(3)   |
|    69    |           7.8381        |           2.0887        |           1.0014        |           2.0858        |AAC->AAA(1), ACA->AAA(1), ACC->AAA(2)AAC(1)ACT(1), ACT->A...|
|    72    |          19.9667        |           0.9422        |           1.0042        |           0.9383        |        AGA->AAA(14)AGG(5)GAA(1), AGG->AAA(2)AGA(5)         |
|    75    |          27.3292        |           0.8584        |           1.0006        |           0.8579        |GTA->AAA(9)ATA(4)ATG(1)GTG(3)GTT(2)TCA(1), GTG->AAA(2)GTA...|
|   151    |          74.1524        |           0.8338        |           0.9990        |           0.8347        |           CAA->AAA(1), CAG->AAA(10)ATG(4)CAA(18)           |
|   162    |          28.9096        |           1.1550        |           0.9816        |           1.1767        |ACT->AAA(1), AGC->AAA(1), AGT->AAA(21)ACT(1)AGC(7)CAT(1)G...|
|   163    |        2461.5837        |           0.9343        |           1.0051        |           0.9296        |        AGC->AAA(13)AGT(9)TCC(1), AGT->AAA(1)AGC(1)         |
|   174    |           8.2639        |           0.8722        |           1.0063        |           0.8667        |AAA->AGA(1)CAA(2), AGA->AAA(3), CAA->AAA(22)AAC(1)AAG(1)A...|
|   181    |          57.3924        |           0.7499        |           0.9986        |           0.7510        |TAC->AAA(2)TAT(2)TGC(1), TAT->AAA(14)ATT(3)TAC(16)TGT(5),...|
|   188    |         903.6130        |           0.7900        |           0.9995        |           0.7905        |         TAT->AAA(7)CAT(2)CTT(1)TAC(1)TTA(2)TTG(1)          |
|   215    |         205.2119        |           0.8392        |           1.0005        |           0.8388        |ACC->AAA(14)AAC(1)ACA(1)ACT(6)GAC(2)TAC(1), ACT->AAA(1)AC...|
|   219    |           8.3712        |           3.2710        |           1.0031        |           3.2609        |     AAA->AAA(15)AAG(15)CAG(1)GAA(1)TGG(1), AAG->AAA(2)     |
|   228    |          10.3951        |           5.6060        |           1.0026        |           5.5916        |AAG->AAA(1), CTC->AAA(1), CTG->AAA(1), CTT->AAA(17)AAG(1)...|

```{r}
object <- '|   Site   |       ER (2 vs 1)       |       ER (3 vs 2)       |   ER (3-island vs 2)    |   ER (3-island vs 3)    |                       Substitutions                        |
|    48    |         106.3661        |           0.7761        |           0.9988        |           0.7770        |ACA->AAA(1), TCA->AAA(4)ACA(8)CAA(1)GAA(2)TCC(1)TCG(2), T...|
|    64    |          13.1124        |           0.9154        |           0.9885        |           0.9261        |  AAA->AAA(2), AAG->AAA(8)AGG(5)CAC(1)TCG(1), AGG->AAA(3)   |
|    69    |           7.8381        |           2.0887        |           1.0014        |           2.0858        |AAC->AAA(1), ACA->AAA(1), ACC->AAA(2)AAC(1)ACT(1), ACT->A...|
|    72    |          19.9667        |           0.9422        |           1.0042        |           0.9383        |        AGA->AAA(14)AGG(5)GAA(1), AGG->AAA(2)AGA(5)         |
|    75    |          27.3292        |           0.8584        |           1.0006        |           0.8579        |GTA->AAA(9)ATA(4)ATG(1)GTG(3)GTT(2)TCA(1), GTG->AAA(2)GTA...|
|   151    |          74.1524        |           0.8338        |           0.9990        |           0.8347        |           CAA->AAA(1), CAG->AAA(10)ATG(4)CAA(18)           |
|   162    |          28.9096        |           1.1550        |           0.9816        |           1.1767        |ACT->AAA(1), AGC->AAA(1), AGT->AAA(21)ACT(1)AGC(7)CAT(1)G...|
|   163    |        2461.5837        |           0.9343        |           1.0051        |           0.9296        |        AGC->AAA(13)AGT(9)TCC(1), AGT->AAA(1)AGC(1)         |
|   174    |           8.2639        |           0.8722        |           1.0063        |           0.8667        |AAA->AGA(1)CAA(2), AGA->AAA(3), CAA->AAA(22)AAC(1)AAG(1)A...|
|   181    |          57.3924        |           0.7499        |           0.9986        |           0.7510        |TAC->AAA(2)TAT(2)TGC(1), TAT->AAA(14)ATT(3)TAC(16)TGT(5),...|
|   188    |         903.6130        |           0.7900        |           0.9995        |           0.7905        |         TAT->AAA(7)CAT(2)CTT(1)TAC(1)TTA(2)TTG(1)          |
|   215    |         205.2119        |           0.8392        |           1.0005        |           0.8388        |ACC->AAA(14)AAC(1)ACA(1)ACT(6)GAC(2)TAC(1), ACT->AAA(1)AC...|
|   219    |           8.3712        |           3.2710        |           1.0031        |           3.2609        |     AAA->AAA(15)AAG(15)CAG(1)GAA(1)TGG(1), AAG->AAA(2)     |
|   228    |          10.3951        |           5.6060        |           1.0026        |           5.5916        |AAG->AAA(1), CTC->AAA(1), CTG->AAA(1), CTT->AAA(17)AAG(1)...|'
HIV_RT_ER_DF <- read_delim(object, delim = '|', trim_ws = TRUE)
```
```{r}
library(reshape2)
HIV_RT_ER_DF %>%  melt(id.vars = "Site", measure.vars = c("ER (2 vs 1)","ER (3 vs 2)","ER (3-island vs 2)","ER (3-island vs 3)")) %>% ggplot()+
  geom_col(aes(x = Site, y = value, fill = variable), position = position_dodge(4))
  #geom_bar(aes(y = value, fill = variable))
```

```{r}
bglobin.obj <- "|   Site   |       ER (2 vs 1)       |       ER (3 vs 2)       |   ER (3-island vs 2)    |   ER (3-island vs 3)    |                       Substitutions                        |
|    10    |          12.9735        |           0.7324        |           0.7297        |           1.0037        |      ACC->CTC(1), ACT->AAT(1)ACC(2)GCT(1)TCT(1)TGT(1)      |
|    42    |          55.7399        |          24.5501        |          24.7731        |           0.9910        |     AGC->CAC(1), AGT->AAC(1), TCC->AGC(2)AGT(1)CAC(1)      |
|    74    |           9.9600        |           1.1959        |           1.1919        |           1.0034        |      AAG->AAA(2)AAT(1)AGC(1)CAG(1), AAT->AGT(1)GCT(1)      |
|    81    |          11.9079        |           6.7999        |           6.8504        |           0.9926        |            AGC->TCC(1), GGC->AAC(1)AGC(1)GGT(1)            |
|    85    |          44.4935        |           0.7913        |           0.7928        |           0.9981        |AAG->ACA(1)AGC(1)CAA(1)CAG(1)GCG(1), AGC->CAT(1), CAA->CA...|
|    87    |         398.6468        |          14.1893        |          14.1004        |           1.0063        |                     AGT->AGC(2)TCC(1)                      |
|   110    |          52.8830        |           0.8326        |           0.8300        |           1.0031        |                  ATT->ATC(3)GTT(2)TGT(2)                   |
|    48    |           1.6586        |           8.7580        |           8.7911        |           0.9962        |         AAT->ACT(1), TCT->AAT(2)ACT(2)AGC(1)CTG(1)         |"

BG_ER_DF <- read_delim(bglobin.obj, delim = '|', trim_ws = TRUE)
```

```{r}
BG_ER_DF %>%  melt(id.vars = "Site", measure.vars = c("ER (2 vs 1)","ER (3 vs 2)","ER (3-island vs 2)","ER (3-island vs 3)")) %>% ggplot()+
  geom_col(aes(x = Site, y = value, fill = variable), position = position_dodge(4))
  #geom_bar(aes(y = value, fill = variable))
```
HIV vif single site

|   Site   |       ER (2 vs 1)       |       ER (3 vs 2)       |   ER (3-island vs 2)    |   ER (3-island vs 3)    |                       Substitutions                        |
|:--------:|:-----------------------:|:-----------------------:|:-----------------------:|:-----------------------:|:----------------------------------------------------------:|
|    6     |           2.2495        |          11.1569        |           1.0014        |          11.1411        |                        CAG->GCA(1)                         |

COX1
### 2 individual sites which showed sufficiently strong preference for multiple-hit models

|   Site   |       ER (2 vs 1)       |       ER (3 vs 2)       |   ER (3-island vs 2)    |   ER (3-island vs 3)    |                       Substitutions                        |
|:--------:|:-----------------------:|:-----------------------:|:-----------------------:|:-----------------------:|:----------------------------------------------------------:|
|   271    |           9.4083        |           1.0009        |           1.0011        |           0.9998        |            GTC->ACC(1)GTA(1)GTT(6), GTT->GTA(1)            |
|   483    |           7.5306        |           1.0012        |           1.0017        |           0.9995        |            GAA->GAG(1)TCA(1), TCA->TCC(1)TCG(1)            |



yokoyama

|   Site   |       ER (2 vs 1)       |       ER (3 vs 2)       |   ER (3-island vs 2)    |   ER (3-island vs 3)    |                       Substitutions                        |
|:--------:|:-----------------------:|:-----------------------:|:-----------------------:|:-----------------------:|:----------------------------------------------------------:|
|    13    |          52.2073        |           0.5929        |           0.8707        |           0.6810        |                        ATG->TTC(2)                         |
|    14    |         150.9647        |           1.8552        |           0.7652        |           2.4244        |ATA->CTC(1), GTA->GTG(1)GTT(1), GTG->TCT(1), TCA->ATA(1)G...|
|    19    |          27.9752        |           0.6240        |           1.0113        |           0.6171        |GTG->ATA(1)ATC(1)CTG(1)GTA(2)GTT(2), GTT->ATC(1)ATT(4)GTA...|
|    26    |          37.3421        |           0.7866        |           0.9703        |           0.8107        |               TAC->GCC(1)TAT(1), TAT->TAC(8)               |
|    35    |           8.0963        |           1.0832        |           0.9637        |           1.1240        |        GCA->GCC(1), GCG->GCA(3)GTG(1), TGG->GCG(1)         |
|    45    |          26.7908        |           0.7598        |           0.9401        |           0.8082        |                     TTC->ATG(1)TTT(2)                      |
|    46    |          14.4686        |           2.1330        |           0.9158        |           2.3290        |      CTG->ATG(1)CTT(1)TTG(1), TTC->ACG(1)CTG(2)TTT(1)      |
|    50    |          18.9419        |           1.0181        |           1.0734        |           0.9485        |ACT->ACC(1), ATT->ATC(2)GTC(1)GTG(1)TTT(2), CTT->CTC(2)CT...|
|    84    |          46.5318        |           0.5237        |           0.8465        |           0.6187        |                  CTC->CAC(1)CAT(1)TTG(3)                   |
|    93    |          52.8115        |           2.9123        |           0.9325        |           3.1230        |               ACC->ACA(2)ACT(1)GTC(1)GTG(1)                |
|    96    |          37.1341        |           3.2911        |           0.9412        |           3.4968        |                     TAC->GTG(1)TAT(2)                      |
|   107    |           9.7138        |           1.2380        |           0.9826        |           1.2599        |CAA->CAG(1), CCA->ACA(1)CAA(1)CCC(3)CGC(1)GAA(1)GTA(1), C...|
|   108    |         101.0508        |           1.8546        |           0.8973        |           2.0669        |ACA->ACG(1), ACG->ACA(2)ACC(1)ACT(3)CTG(1)GTA(1), CTC->TT...|
|   122    |          17.8947        |           1.9526        |           0.9081        |           2.1502        |      GAA->CAA(1)GAG(2), GAG->ATC(1)ATG(1)CAG(1)GAA(3)      |
|   136    |          71.0212        |           0.6404        |           0.9599        |           0.6671        |           TAC->TAT(1), TAT->TAC(2), TGG->TAT(2)            |
|   144    |         318.8699        |           0.7403        |           1.1404        |           0.6491        |         AGC->ACC(1)GCC(2)TCC(1), GCC->GAA(1)TCC(1)         |
|   149    |          22.8614        |           2.3053        |           0.9619        |           2.3966        |      GGG->ACT(1)CAG(1)GGA(5)GGC(1)GGT(2), GGT->GGC(1)      |
|   158    |          14.1189        |           3.0228        |           0.9465        |           3.1938        |GCA->ACG(1)ATG(1), GCC->ACC(1)AGT(1)ATC(1)ATG(1)GCA(1)GCG...|
|   160    |          28.9554        |           1.2120        |           1.3124        |           0.9235        |            ACC->ACA(2)ACT(1)TCC(2), TCC->AGC(1)            |
|   162    |          42.3805        |           0.5871        |           1.1305        |           0.5193        |ATC->ACC(1)ATA(1)ATT(1)GTC(3)TTG(1), GGT->GCC(1), GTA->CT...|
|   163    |          20.8949        |           0.8189        |           0.9566        |           0.8560        |                     ATG->GCG(1)TTG(1)                      |
|   165    |          10.1073        |           1.5528        |           0.9650        |           1.6090        |CTG->ATG(1), TCC->GGC(1)TGC(1), TCG->TCC(2), TTG->AAT(1)A...|
|   195    |          41.9450        |           1.6128        |           0.9415        |           1.7131        |AAG->AAC(1)ACC(1)CAC(1)GCC(1)GCG(1), CAC->CGC(1), GCC->AC...|
|   196    |           9.5755        |           1.9173        |           0.9614        |           1.9942        |CAG->CCC(1)GAG(1), CCC->CAG(1), CCG->CCA(1), CCT->CCC(1)C...|
|   209    |           9.2534        |           1.0200        |           1.0889        |           0.9367        |ACC->ACA(1), ATC->ACC(1)ATA(1), ATT->CTT(1), GTC->ACC(1)A...|
|   210    |          78.1724        |           3.0818        |           0.9327        |           3.3040        |CTC->GTG(1)TTA(1), GTC->GTG(2)GTT(3)TGC(2), GTT->GTC(1), ...|
|   213    |          22.7746        |           0.5560        |           0.9739        |           0.5709        |ACC->ATC(2)ATG(1)GTC(1)TCC(2), ATC->ATA(1)ATT(1)CTG(2)TCC...|
|   236    |          45.2105        |           5.0861        |           0.9490        |           5.3591        |               CAG->CAA(1)GCC(1), GCC->GCT(1)               |
|   264    |          32.4793        |           1.1110        |           0.9455        |           1.1750        |        ACC->ACA(1), TGC->ACC(1)TGT(4), TGT->TGC(1)         |
|   270    |         216.0457        |          13.2258        |          11.3947        |           1.1607        |   AGC->AGT(5)GGA(1)GGC(3)GGG(1)TAT(1)TCA(1), GGC->GGA(1)   |
|   271    |          51.2877        |           1.6525        |           0.9532        |           1.7336        |      GTG->ACC(1)ACG(1)GTA(1)GTC(1)GTT(2), GTT->GTC(1)      |
|   273    |           9.7226        |           0.9912        |           0.9105        |           1.0887        |                     TGG->GCG(1)TTC(1)                      |
|   274    |          95.5793        |           0.5156        |           0.9282        |           0.5555        |            TAC->TAT(2)TTC(2), TAT->TAC(4)TGG(3)            |
|   277    |         121.9976        |           1.9885        |           0.8298        |           2.3963        |   ACA->ACG(1)TGT(1), ACC->ACA(1)ACT(1)AGC(1)TGC(2)TTC(1)   |
|   282    |          94.8591        |           1.3634        |           0.9965        |           1.3681        |ACA->ACT(2), ACT->AGC(1), GAA->AAC(1)ACA(1)GAC(1)GAG(7), ...|
|   297    |           8.8674        |           3.4665        |           0.7715        |           4.4931        |  ACT->ACG(1), AGC->ACC(2)ACT(1)AGT(4)GCT(1), AGT->ACT(1)   |
|   311    |          47.4661        |           0.7582        |           0.9647        |           0.7860        |               AAA->AAG(1), AAG->AAA(1)AGT(1)               |
|   281    |           4.3164        |          39.0412        |          60.0429        |           0.6502        |ACC->ACA(1)AGC(1)GCC(1), TCA->TCG(1), TCC->TTC(1), TCT->A...|

```{r}
yokoyama.obj <- "|   Site   |       ER (2 vs 1)       |       ER (3 vs 2)       |   ER (3-island vs 2)    |   ER (3-island vs 3)    |                       Substitutions                        |
|    13    |          52.2073        |           0.5929        |           0.8707        |           0.6810        |                        ATG->TTC(2)                         |
|    14    |         150.9647        |           1.8552        |           0.7652        |           2.4244        |ATA->CTC(1), GTA->GTG(1)GTT(1), GTG->TCT(1), TCA->ATA(1)G...|
|    19    |          27.9752        |           0.6240        |           1.0113        |           0.6171        |GTG->ATA(1)ATC(1)CTG(1)GTA(2)GTT(2), GTT->ATC(1)ATT(4)GTA...|
|    26    |          37.3421        |           0.7866        |           0.9703        |           0.8107        |               TAC->GCC(1)TAT(1), TAT->TAC(8)               |
|    35    |           8.0963        |           1.0832        |           0.9637        |           1.1240        |        GCA->GCC(1), GCG->GCA(3)GTG(1), TGG->GCG(1)         |
|    45    |          26.7908        |           0.7598        |           0.9401        |           0.8082        |                     TTC->ATG(1)TTT(2)                      |
|    46    |          14.4686        |           2.1330        |           0.9158        |           2.3290        |      CTG->ATG(1)CTT(1)TTG(1), TTC->ACG(1)CTG(2)TTT(1)      |
|    50    |          18.9419        |           1.0181        |           1.0734        |           0.9485        |ACT->ACC(1), ATT->ATC(2)GTC(1)GTG(1)TTT(2), CTT->CTC(2)CT...|
|    84    |          46.5318        |           0.5237        |           0.8465        |           0.6187        |                  CTC->CAC(1)CAT(1)TTG(3)                   |
|    93    |          52.8115        |           2.9123        |           0.9325        |           3.1230        |               ACC->ACA(2)ACT(1)GTC(1)GTG(1)                |
|    96    |          37.1341        |           3.2911        |           0.9412        |           3.4968        |                     TAC->GTG(1)TAT(2)                      |
|   107    |           9.7138        |           1.2380        |           0.9826        |           1.2599        |CAA->CAG(1), CCA->ACA(1)CAA(1)CCC(3)CGC(1)GAA(1)GTA(1), C...|
|   108    |         101.0508        |           1.8546        |           0.8973        |           2.0669        |ACA->ACG(1), ACG->ACA(2)ACC(1)ACT(3)CTG(1)GTA(1), CTC->TT...|
|   122    |          17.8947        |           1.9526        |           0.9081        |           2.1502        |      GAA->CAA(1)GAG(2), GAG->ATC(1)ATG(1)CAG(1)GAA(3)      |
|   136    |          71.0212        |           0.6404        |           0.9599        |           0.6671        |           TAC->TAT(1), TAT->TAC(2), TGG->TAT(2)            |
|   144    |         318.8699        |           0.7403        |           1.1404        |           0.6491        |         AGC->ACC(1)GCC(2)TCC(1), GCC->GAA(1)TCC(1)         |
|   149    |          22.8614        |           2.3053        |           0.9619        |           2.3966        |      GGG->ACT(1)CAG(1)GGA(5)GGC(1)GGT(2), GGT->GGC(1)      |
|   158    |          14.1189        |           3.0228        |           0.9465        |           3.1938        |GCA->ACG(1)ATG(1), GCC->ACC(1)AGT(1)ATC(1)ATG(1)GCA(1)GCG...|
|   160    |          28.9554        |           1.2120        |           1.3124        |           0.9235        |            ACC->ACA(2)ACT(1)TCC(2), TCC->AGC(1)            |
|   162    |          42.3805        |           0.5871        |           1.1305        |           0.5193        |ATC->ACC(1)ATA(1)ATT(1)GTC(3)TTG(1), GGT->GCC(1), GTA->CT...|
|   163    |          20.8949        |           0.8189        |           0.9566        |           0.8560        |                     ATG->GCG(1)TTG(1)                      |
|   165    |          10.1073        |           1.5528        |           0.9650        |           1.6090        |CTG->ATG(1), TCC->GGC(1)TGC(1), TCG->TCC(2), TTG->AAT(1)A...|
|   195    |          41.9450        |           1.6128        |           0.9415        |           1.7131        |AAG->AAC(1)ACC(1)CAC(1)GCC(1)GCG(1), CAC->CGC(1), GCC->AC...|
|   196    |           9.5755        |           1.9173        |           0.9614        |           1.9942        |CAG->CCC(1)GAG(1), CCC->CAG(1), CCG->CCA(1), CCT->CCC(1)C...|
|   209    |           9.2534        |           1.0200        |           1.0889        |           0.9367        |ACC->ACA(1), ATC->ACC(1)ATA(1), ATT->CTT(1), GTC->ACC(1)A...|
|   210    |          78.1724        |           3.0818        |           0.9327        |           3.3040        |CTC->GTG(1)TTA(1), GTC->GTG(2)GTT(3)TGC(2), GTT->GTC(1), ...|
|   213    |          22.7746        |           0.5560        |           0.9739        |           0.5709        |ACC->ATC(2)ATG(1)GTC(1)TCC(2), ATC->ATA(1)ATT(1)CTG(2)TCC...|
|   236    |          45.2105        |           5.0861        |           0.9490        |           5.3591        |               CAG->CAA(1)GCC(1), GCC->GCT(1)               |
|   264    |          32.4793        |           1.1110        |           0.9455        |           1.1750        |        ACC->ACA(1), TGC->ACC(1)TGT(4), TGT->TGC(1)         |
|   270    |         216.0457        |          13.2258        |          11.3947        |           1.1607        |   AGC->AGT(5)GGA(1)GGC(3)GGG(1)TAT(1)TCA(1), GGC->GGA(1)   |
|   271    |          51.2877        |           1.6525        |           0.9532        |           1.7336        |      GTG->ACC(1)ACG(1)GTA(1)GTC(1)GTT(2), GTT->GTC(1)      |
|   273    |           9.7226        |           0.9912        |           0.9105        |           1.0887        |                     TGG->GCG(1)TTC(1)                      |
|   274    |          95.5793        |           0.5156        |           0.9282        |           0.5555        |            TAC->TAT(2)TTC(2), TAT->TAC(4)TGG(3)            |
|   277    |         121.9976        |           1.9885        |           0.8298        |           2.3963        |   ACA->ACG(1)TGT(1), ACC->ACA(1)ACT(1)AGC(1)TGC(2)TTC(1)   |
|   282    |          94.8591        |           1.3634        |           0.9965        |           1.3681        |ACA->ACT(2), ACT->AGC(1), GAA->AAC(1)ACA(1)GAC(1)GAG(7), ...|
|   297    |           8.8674        |           3.4665        |           0.7715        |           4.4931        |  ACT->ACG(1), AGC->ACC(2)ACT(1)AGT(4)GCT(1), AGT->ACT(1)   |
|   311    |          47.4661        |           0.7582        |           0.9647        |           0.7860        |               AAA->AAG(1), AAG->AAA(1)AGT(1)               |
|   281    |           4.3164        |          39.0412        |          60.0429        |           0.6502        |ACC->ACA(1)AGC(1)GCC(1), TCA->TCG(1), TCC->TTC(1), TCT->A...|"

yoko_ER_DF <- read_delim(yokoyama.obj, delim = '|', trim_ws = TRUE)
```

```{r}
yoko_ER_DF %>%  melt(id.vars = "Site", measure.vars = c("ER (2 vs 1)","ER (3 vs 2)","ER (3-island vs 2)","ER (3-island vs 3)")) %>% ggplot()+
  geom_col(aes(x = Site, y = value, fill = variable), position = position_dodge(4)) + coord_cartesian(ylim = c(0,15))
  #geom_bar(aes(y = value, fill = variable))
```

```{r}
yoko_ER_DF$`ER (2 vs 1)` %>% max()
yoko_ER_DF$`ER (2 vs 1)` %>% which.max()

which(log(yoko_ER_DF$`ER (2 vs 1)`) > 2) %>% length()

which(log(yoko_ER_DF$`ER (3 vs 2)`) > 2) %>% yoko_ER_DF$Site[.]
which(log(yoko_ER_DF$`ER (3 vs 2)`) > 2) %>% yoko_ER_DF$`ER (3 vs 2)`[.]

which(log(yoko_ER_DF$`ER (3-island vs 2)`) > 2) %>% yoko_ER_DF$Site[.]
which(log(yoko_ER_DF$`ER (3-island vs 2)`) > 2) %>% yoko_ER_DF$`ER (3-island vs 2)`[.]


which(log(yoko_ER_DF$`ER (3-island vs 3)`) > 2) %>% yoko_ER_DF$Site[.]
which(log(yoko_ER_DF$`ER (3-island vs 3)`) > 2) %>% yoko_ER_DF$`ER (3-island vs 3)`[.]
```

