---
title: "Selectome_v_Petrov_branch_lengths"
author: "sadie"
date: "9/20/2019"
output:
  pdf_document: default
  html_document: default
---


```{r, message=FALSE, warning=FALSE,}
library(readr)
library(dplyr)
library(ggplot2)
library(stringr)
library(plotly)
library(tidyr)

```

```{r load libraries and data, message=FALSE, warning=FALSE, cache=TRUE}


selectome.dat <- read_csv("~/Downloads/SELECTOME_SRV_nr_v02.csv")

petrov.dat <- read_csv("~/Downloads/PETROV_SRV_nr_v02.csv")

schultz.dat <- read_csv("~/Downloads/IMMUNE_SRV_nr_v02.csv")

```






## put branch length estimates for each model in own column for each branch 
## Lengthx1 - the branch length according to Standard MG94
## Lengthx2 - the branch length according to the double hit MG94
## Lengthx3 - the branch length according to the triple hit MG94
```{r, cache=TRUE}
attach(selectome.dat)
temp.2 <- selectome.dat %>% separate_rows(., `Branch Attributes - MG94 with double and triple instantaneous substitutions`,`Branch Attributes - MG94 with double instantaneous substitutions`, `Branch Attributes - Standard MG94`, sep = ",")

temp.2 <- temp.2 %>% separate(`Branch Attributes - MG94 with double and triple instantaneous substitutions`, c("Branchx3", "Lengthx3"), sep = ":", convert = TRUE)

temp.2 <- temp.2 %>% separate(`Branch Attributes - MG94 with double instantaneous substitutions`, c("Branchx2", "Lengthx2"), sep = ":", convert = TRUE)

temp.2 <- temp.2 %>% separate(`Branch Attributes - Standard MG94`, c("Branchx1", "Lengthx1"), sep = ":", convert = TRUE)


temp.2$Branch <- temp.2$Branchx3 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim()


temp.2$Lengthx1 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim() -> temp.2$Lengthx1

temp.2$Lengthx2 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim() -> temp.2$Lengthx2

temp.2$Lengthx3 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim() -> temp.2$Lengthx3

sel.dat.bl <- temp.2
```

## put branch length estimates for each model in own column for each branch 
## Lengthx1 - the branch length according to Standard MG94
## Lengthx2 - the branch length according to the double hit MG94
## Lengthx3 - the branch length according to the triple hit MG94
```{r, cache=TRUE}
attach(petrov.dat)
temp.2 <- petrov.dat %>% separate_rows(., `Branch Attributes - MG94 with double and triple instantaneous substitutions`,`Branch Attributes - MG94 with double instantaneous substitutions`, `Branch Attributes - Standard MG94`, sep = ",")

temp.2 <- temp.2 %>% separate(`Branch Attributes - MG94 with double and triple instantaneous substitutions`, c("Branchx3", "Lengthx3"), sep = ":", convert = TRUE)

temp.2 <- temp.2 %>% separate(`Branch Attributes - MG94 with double instantaneous substitutions`, c("Branchx2", "Lengthx2"), sep = ":", convert = TRUE)

temp.2 <- temp.2 %>% separate(`Branch Attributes - Standard MG94`, c("Branchx1", "Lengthx1"), sep = ":", convert = TRUE)


temp.2$Branch <- temp.2$Branchx3 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim()


temp.2$Lengthx1 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim() -> temp.2$Lengthx1

temp.2$Lengthx2 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim() -> temp.2$Lengthx2

temp.2$Lengthx3 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim() -> temp.2$Lengthx3

pet.dat.bl <- temp.2
```

## put branch length estimates for each model in own column for each branch for IMMUNE/Schultz
## Lengthx1 - the branch length according to Standard MG94
## Lengthx2 - the branch length according to the double hit MG94
## Lengthx3 - the branch length according to the triple hit MG94
```{r, cache=TRUE}
attach(schultz.dat)
temp.2 <- schultz.dat %>% separate_rows(., `Branch Attributes - MG94 with double and triple instantaneous substitutions`,`Branch Attributes - MG94 with double instantaneous substitutions`, `Branch Attributes - Standard MG94`, sep = ",")

temp.2 <- temp.2 %>% separate(`Branch Attributes - MG94 with double and triple instantaneous substitutions`, c("Branchx3", "Lengthx3"), sep = ":", convert = TRUE)

temp.2 <- temp.2 %>% separate(`Branch Attributes - MG94 with double instantaneous substitutions`, c("Branchx2", "Lengthx2"), sep = ":", convert = TRUE)

temp.2 <- temp.2 %>% separate(`Branch Attributes - Standard MG94`, c("Branchx1", "Lengthx1"), sep = ":", convert = TRUE)


temp.2$Branch <- temp.2$Branchx3 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim()


temp.2$Lengthx1 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim() -> temp.2$Lengthx1

temp.2$Lengthx2 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim() -> temp.2$Lengthx2

temp.2$Lengthx3 %>% str_remove_all("'") %>% str_remove("\\{") %>% str_remove("\\}") %>% str_trim() -> temp.2$Lengthx3

schultz.dat.bl <- temp.2
```

```{r}
pet.dat.bl %>% ggplot()+ geom_histogram(aes(as.numeric(Lengthx1)), binwidth = 0.01, fill = "red", alpha = 0.5)+ coord_cartesian(xlim = c(0,0.5))
sel.dat.bl %>% filter(as.numeric(Lengthx1 )!= 0) %>% ggplot()+ geom_histogram(aes(as.numeric(Lengthx1)), binwidth = 0.01, fill = "blue", alpha = 0.5)+ xlim(0,0.5)

ggplot()+ geom_histogram(data = sel.dat.bl, aes(x =as.numeric(Lengthx1),  y = (..count..)/sum(..count..)), binwidth = 0.01, fill = "blue", alpha = 0.5)+ xlim(0,0.5)+ geom_histogram(data = pet.dat.bl, aes(x =as.numeric(Lengthx1),  y = (..count..)/sum(..count..)), binwidth = 0.01, fill = "red", alpha = 0.5) + labs(x = "branch lengths (MG94)")+ geom_histogram(data = schultz.dat.bl, aes(x =as.numeric(Lengthx1),  y = (..count..)/sum(..count..)), binwidth = 0.01, fill = "yellow", alpha = 0.5) + labs(x = "branch lengths (MG94)")

```

```{r}
summary(sel.dat.bl$Lengthx1 %>% as.numeric())

summary(pet.dat.bl$Lengthx1 %>% as.numeric())

summary(schultz.dat.bl$Lengthx1 %>% as.numeric())
```

```{r}
comb.length <- bind_rows(
  sel.dat.bl %>% select(Lengthx1) %>% mutate(dataset = "Selectome"),
  pet.dat.bl %>% select(Lengthx1) %>% mutate(dataset = "Petrov"),
  schultz.dat.bl %>% select(Lengthx1) %>% mutate(dataset = "Schultz")
  )
```

```{r}
comb.length %>% ggplot()+geom_boxplot(aes(y = as.numeric(Lengthx1), x = dataset)) + coord_cartesian(ylim = c(0,0.15)) + labs(y = "branch length (mg94)")

```
```{r}
comb.length %>% filter(Lengthx1 %>% as.numeric() <=2) %>% ggplot()+geom_violin(aes(y = as.numeric(Lengthx1), x = dataset), scale = "count")  + labs(y = "branch length (mg94)")
```

#explore other variables
##sequence length comparasion 

### histogram of number of sites
```{r}
ggplot()+ geom_histogram(data = selectome.dat, aes(x = `number of sites`,  y = (..count..)/sum(..count..)), binwidth = 10, fill = "blue", alpha = 0.5)+ geom_histogram(data = petrov.dat, aes(x =`number of sites`,  y = (..count..)/sum(..count..)), binwidth = 10, fill = "red", alpha = 0.5) + labs(x = "number of sites")+ geom_histogram(data = schultz.dat, aes(x =`number of sites`,  y = (..count..)/sum(..count..)), binwidth = 10, fill = "yellow", alpha = 0.5) 
```

not clear if there is any difference here. maybe selectome is a little shorter
let's look at numbers

```{r}
summary(selectome.dat$`number of sites`)

summary(petrov.dat$`number of sites`)

summary(schultz.dat$`number of sites`)
```

```{r}
comb.length <- bind_rows(
  selectome.dat %>% select(`number of sites`) %>% mutate(dataset = "Selectome"),
  petrov.dat %>% select(`number of sites`) %>% mutate(dataset = "Petrov"),
  schultz.dat %>% select(`number of sites`) %>% mutate(dataset = "Schultz")
  )
```


```{r}
comb.length  %>% ggplot()+geom_violin(aes(y = `number of sites`, x = dataset), scale = "count")  + labs(y = "number of sites")
```

